### 2024-04-10 tesis_Ashish/Chapter4/chapter4.tex
update 11 Apr

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=1\textwidth]{ashish_thesis/PCC_lin_2018.png}
  \caption[2018 PCC linearity]{Linearity of PCC compared to HFOC for fill 6961. Ratio of PCC/HFOC luminosity plotted as a function of HFOC luminosity to determine change in detector response over different luminosity levels. Slope of the linear fit is 0.00154614 in units of (Hz/ub)^{-1}.}
  \label{fig:stabprof2}
\end{figure}
